Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-02 bbbq_article.tex
Add stats

The first query was a call to the 'gene' database for the 
term 'membrane protein' (in all fields) for the organism \textbf{Homo sapiens}.
This resulted in 1129 gene IDs.
The next query was a call to the 'gene' database 
to obtain the gene names from the gene IDs.
Per gene name, the 'dbSNP' NCBI database is queried for 
variations associated with the gene name.

@@

>>>>

The first query was a call to the 'gene' database for the 
term 'membrane protein' (in all fields) for the organism \textbf{Homo sapiens}.
This resulted in 1077 gene IDs
\richel{
  This was December 2020.
  At 2021-03-01, one will get 1130 gene IDs.
  Also, one of the gene IDs that was valid back then,
  has been obsoleted.
}.
The next query was a call to the 'gene' database 
to obtain the gene names from the gene IDs.
Per gene name, the 'dbSNP' NCBI database is queried for 
variations associated with the gene name.

@@

% \paragraph{Statistics}

Table \ref{tab:snp_stats} shows the statistics for all
SNPs, where tables \ref{tab:snp_stats_per_spanner_single}
and \ref{tab:snp_stats_per_spanner_multi} show the
statistics for only single-spanners and multi-spanners respectively.
These probabilities are also displayed visually in 
figures \ref{fig:ppoisbinom} (all proteins), \ref{fig:ppoisbinom_single} (single-spanners)
and \ref{fig:ppoisbinom_multi} (multi-spanners).

% Label: tab:snp_stats
\input{ncbi_peregrine_results/snp_stats.tex}

% Label: tab:snp_stats_per_spanner_single
\input{ncbi_peregrine_results/snp_stats_per_spanner_single.tex}

% Label: tab:snp_stats_per_spanner_multi
\input{ncbi_peregrine_results/snp_stats_per_spanner_multi.tex}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/ppoisbinom.png}
  \caption{
    Probabilities for all SNPs
  }
  \label{fig:ppoisbinom}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/ppoisbinom_single.png}
  \caption{
    Probabilities for SNPs in single-spanners
  }
  \label{fig:ppoisbinom_single}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/ppoisbinom_multi.png}
  \caption{
    Probabilities for SNPs in multi-spanners
  }
  \label{fig:ppoisbinom_multi}
\end{figure}
